### 2019-03-14 proposals/TESS_GI_cycle02/tessgi_gully_cycle2.tex
pre CVM feedback

\usepackage[backref,breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\bibliographystyle{plainnat}
%\usepackage{cleveref}
\input{mgs_setup}

@@

@@

\begin{center}
\bfseries\uppercase{%
%%
%% ENTER TITLE OF PROPOSAL BELOW THIS LINE
Starspots confound derived stellar properties and a strategy for probabilistic mitigation
%%
%%
}
\end{center}

@@

Here we propose a strategy for mitigating starspot-induced exoplanet radius biases, based on a large sample of spotted stars observed in \tess\ Cycle 2.  The approach will deliver constraints on both the typical starspot coverage fraction and the typical starspot temperature contrast, as a function of spectral type and rotation rate.  This mapping can then serve as a ``lookup table'' for practitioners to gauge the extent to which a given source is likely to suffer from starspot-induced exoplanet radius biases.  No such reliable lookup table presently exists for main sequence stars, owing to the inability of differential lightcurves to account for \emph{total} starspot coverage fractions \citep{2018ApJ...865..142B}.

@@

\begin{figure}
\includegraphics[width=0.95\textwidth]{figures/multi_panel.pdf}
\caption{Prediction for \tess\ amplitudes relative to the \kepler\ sample.}
\label{fig:predictAmps}
\end{figure}

>>>>

\usepackage[backref,breaklinks,colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\bibliographystyle{plainnat}
%\bibliographystyle{yahapj}
%\usepackage{cleveref}
\input{mgs_setup}

@@

\usepackage{paralist}
\makeatletter
\newcommand{\mybullet}{%
    \ifnum\value{enumi}=1
    \else
        \textbullet
    \fi
}
\makeatother
\renewenvironment{thebibliography}[1]{\let\par\relax%
  \section*{\refname}\inparaenum[\mybullet]}{\endinparaenum}
\let\oldbibitem\bibitem
\renewcommand{\bibitem}{\item \oldbibitem}
\include{JournalAbbr}

@@

\begin{center}
\bfseries\uppercase{%
%%
%% ENTER TITLE OF PROPOSAL BELOW THIS LINE
Mitigating exoplanet density biases from wavelength dependence of spot contrast
%%
%%
}
\end{center}

@@

Recent work has shown that ignoring starspots biases measurements of exoplanet radii \citep{2018ApJ...853..122R}.  Here we propose a strategy for mitigating starspot-induced exoplanet radius biases, based on a large sample of spotted stars observed in \tess\ Cycle 2.  The approach will deliver constraints on both the typical starspot coverage fraction and the typical starspot temperature contrast, as a function of spectral type and rotation rate.  This mapping can then serve as a ``lookup table'' for practitioners to gauge the extent to which a given source is likely to suffer from starspot-induced exoplanet radius biases.  No such reliable lookup table presently exists for main sequence stars, owing to the inability of differential lightcurves to account for \emph{total} starspot coverage fractions \citep{2018ApJ...865..142B}.

@@

\begin{figure}[hbt!]
\includegraphics[width=0.95\textwidth]{figures/multi_panel.pdf}
\caption{\texttt{A)} Schematic of a planet ($R_p = 0.1 R_\star$) transiting a star with unocculted starspots as the star moves from left to right.  \texttt{B)} The resulting transit depth shows a systematic bias and a wavelength dependence due to starspots. \texttt{C)} Illustration of \texttt{D)} Prediction for \tess\ amplitudes (colorful contours) relative to the \kepler\ sample (gray shaded background contours and black points) for $4000 < T_{phot} (K) < 4500$ \citep{2014ApJS..211...24M}.}
\label{fig:predictAmps}
\end{figure}
